\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{needspace}

\pagestyle{empty}
\raggedbottom
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    pdfauthor={Amarnath Reddy Malkireddy},
    pdftitle={Resume - Amarnath Reddy Malkireddy}
}

\titleformat{\section}{\bfseries\large\scshape}{}{0em}{}[\vspace{-3pt}\titlerule]
\titlespacing*{\section}{0pt}{*1.2}{*0.4}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, label=\textbullet, itemsep=2pt, topsep=2pt, partopsep=0pt, parsep=0pt}
\newcommand{\dateright}[1]{\hfill{\small\textit{#1}}}
\newcommand{\sectionneed}{\Needspace{3\baselineskip}}
\newcommand{\afterheader}{\vspace{-6pt}}

\begin{document}

\begin{center}
    {\LARGE\bfseries Amarnath Reddy Malkireddy}\\[-2pt]
    Albany, NY \textbullet{} (838) 200-7053 \textbullet{}
    \href{mailto:mamarnathreddy49@gmail.com}{amarnathreddymalkireddy@gmail.com} 
    \href{https://www.linkedin.com/in/amarnath-reddy-malkireddy}{linkedin.com/in/amarnath-reddy-malkireddy}
\end{center}
\afterheader

\sectionneed
\section*{Professional Summary}
Results-driven Data Analyst with 5 years of progressively responsible experience in transforming complex data into actionable insights across healthcare, government, telecom, and retail sectors. Adept at building scalable ETL pipelines, predictive models, and real-time dashboards using Python, SQL, Tableau, and Power BI. Skilled in leveraging cloud platforms (AWS, GCP), implementing CI/CD workflows, and ensuring compliance with HIPAA, SOX, and FERPA standards. Proven track record of using AI-driven tools like GPT APIs to streamline reporting and accelerate business decisions. Strong collaborator with a passion for data storytelling, automation, and driving data-first strategies.


\sectionneed
\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Programming:} Python (Pandas, NumPy, Scikit-learn), R, SQL (PostgreSQL, BigQuery, Redshift), Bash.
    \item \textbf{Cloud Platforms:} AWS (S3, Glue, Lambda, Redshift), GCP (BigQuery, Cloud Functions), Snowflake.
    \item \textbf{Data Engineering:} ETL/ELT pipelines, dbt, Airflow, REST APIs, data modeling, Data Warehousing.
    \item \textbf{Visualization:} Tableau, Power BI, Looker, Google Data Studio, Excel (Pivot, Power Query, VBA).
    \item \textbf{Machine Learning:} Regression, Classification, ARIMA, Clustering, Forecasting, Anomaly Detection.
    \item \textbf{DevOps \& Automation:} Git, GitHub Actions, Docker (Basics), CI/CD pipelines, Terraform (familiar).
    \item \textbf{Infrastructure:} Linux, Kubernetes (Basics), Flask APIs.
    \item \textbf{Governance:} HIPAA, FERPA, SOX/PCI DSS, SLA/QoS, metadata management.
    \item \textbf{Generative AI:} GPT API for report automation, workflow acceleration, and narrative generation.
\end{itemize}

\sectionneed
\section*{Professional Experience}

\noindent\textbf{Bioinformatics Data Analyst} \dateright{May 2024 – Present}\\
\textit{US Tech Solutions (Client: NYS Dept. of Health), Albany, NY}
\begin{itemize}
    \item Developed GCP-based ETL pipelines processing 200K+ monthly EHR records via FHIR APIs, improving data access by 65\%.
    \item Built 8+ Tableau/Looker dashboards for real-time capacity metrics, cutting manual reporting time by 40\%.
    \item Automated dbt workflows with testing and lineage tracking, reducing pipeline failures by 30\%.
    \item Integrated anomaly detection using SQL + Python, reducing critical data errors by 25\%.
    \item Leveraged GPT APIs to auto-generate narrative reports, accelerating reporting cycles by 25\%.
\end{itemize}

\vspace{2pt}
\noindent\textbf{Data Analyst Intern} \dateright{May 2022 – Aug 2022}\\
\textit{University at Albany, Albany, NY}
\begin{itemize}
    \item Consolidated academic datasets using Python + Power Query, boosting data reliability by 30\%.
    \item Built PostgreSQL dashboards for retention analytics; supported targeted outreach efforts across departments.
    \item Led Tableau/SQL workshops for 15+ internal teams to democratize data access and improve operations.
\end{itemize}

\vspace{2pt}
\noindent\textbf{Application Development Analyst} \dateright{May 2019 – Dec 2021}\\
\textit{Accenture, Hyderabad, India}
\begin{itemize}
    \item Delivered AWS data pipelines (S3, Glue, Redshift) for telecom client supporting 2M+ records daily.
    \item Analyzed SLA/QoS metrics to improve operations by 15\% using Python dashboards.
    \item Built SOX-compliant dashboards and supported fraud detection analysis, reducing risk by 10\%.
    \item Created churn prediction models (80\% accuracy) that improved customer retention by 20\%.
    \item Mentored 4 junior analysts and promoted Agile processes using Git and JIRA.
\end{itemize}

\sectionneed
\section*{Projects}

\noindent\textbf{Resume \& Application Automation (Personal Project)}\\
\begin{itemize}
    \item Built Python CLI using GPT API to generate tailored resumes and cover letters, reducing application time by 60\%.
    \item Deployed automation via GitHub Actions (CI/CD) to scan jobs and trigger resume tailoring pipelines.
\end{itemize}

\vspace{2pt}
\noindent\textbf{COVID-19 Hospitalization Forecasting (Capstone Project)}\\
\begin{itemize}
    \item Modeled hospitalization demand using ARIMA and XGBoost for pandemic planning.
    \item Built Tableau dashboards with stakeholder simulation and alerting capability.
\end{itemize}

\vspace{2pt}
\noindent\textbf{Customer Churn Exploration (Kaggle-style)}\\
\begin{itemize}
    \item Created end-to-end pipeline using Snowflake + PostgreSQL; modeled churn with Logistic Regression + XGBoost.
    \item Deployed scoring API with Flask + AWS Lambda; visualized results in Power BI with executive-ready insights.
\end{itemize}

\sectionneed
\section*{Education}
\textbf{M.S. in Data Science}, University at Albany, SUNY \dateright{Dec 2023}\\
\textit{Relevant Coursework:} Machine Learning, Data Mining, Statistical Computing, Big Data Analytics

\sectionneed
\section*{Certifications}
\begin{itemize}
    \item Python for Data Science, AI, and Development – IBM
    \item Data Visualization and Dashboards with Excel and Cognos – IBM
    \item Introduction to Data Analytics – IBM
    \item Excel Basics for Data Analysis – IBM
    \item PCEP – Certified Entry-Level Python Programmer – Python Institute
    \item AZ-900: Microsoft Azure Fundamentals – Microsoft
\end{itemize}

\end{document}
